Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-08 manuscripts/supplement.Rmd
update supplement

```{r quadraticcosts, include=FALSE, message=FALSE}
source("components/quad_costs.R")
```

@@

labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))

ex <- dt_quad %>% 
  filter(replicate=="rep_17" & time < OptTime) %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, 
                       name="")

>>>>

```{r quadraticcosts, include=FALSE, message=FALSE}

source("components/quad_costs.R")
```

@@

labels <- c(harvest = substitute(paste("Harvest Policy under ", paste(Pi[4]))), 
                                harvest_alt = substitute(paste("Harvest under ", paste(Pi[0]), " (Reed)")))
ex <- dt_quad %>% 
  filter(replicate=="rep_17" & time < OptTime) %>%
  select(time, harvest, harvest_alt) %>%
  gather(variable, stock, -time) 
ggplot(ex) + 
  geom_line(aes(time, stock, col=variable), lwd=1) + 
  scale_color_discrete(labels=labels, 
                       name="")
